Re-analysis of B&S with both smoothed and empirical AUC-ROC

### 2020-11-13 rep_nosmooth/README.Rmd
don't change working directories in analysis scripts
Use here() directly for the input/output files instead of changing working directories at the top of each script.

---
title: "Replication materials for Beger, Morgan, Ward, nd"
output: 
  github_document
always_allow_html: true
---

@@

**tl;dr:** run through `master.R`

@@

Below are instructions for how to run the script in order to replicate the updated analysis. To do a clean replication, delete the `output/` folder; this is not required though.

@@

Anyways, the model runner script does include a provision for setting a RNG seed, in which case the key output files will be suffixed with the RNG seed value. Note that the results processing scripts are not setup to work this these output files, but it should be fairly obvious what lines need modifications to make them work.

>>>>

---
title: "Re-analysis of B&S with both smoothed and empirical AUC-ROC"
output: 
  github_document
always_allow_html: true
---

@@

The easiest way to reproduce our re-analysis is to run `master.R`, which will 
run the other scripts in correct order.

- Adjust the number of parallel workers in `2-model-runner.R`
- Go through `master.R`.

If you want to run without `master.R`, the numbers in the other R scripts
indicate dependence. For example, the script starting with "3-" for requires 
all "1-" and "2-" scripts to have been run.

Our re-analysis is based on the original B&S replication materials. The main
substantive changes are:

- We evaluate AUC values from both the original smoothed ROC curves but also
  standard empirical ROC curves.
- Two of the structural model implementations have been changed.

While the substantive changes are minor, we have changed the structure of the
code substantially so that the random forest models can be run in parallel.

We intentionally do not set a RNG seed, since the substantive conclusions
of our re-analysis should not depend on particular RNG seed values. There is
some slight variation between re-runs of the models as a result. There is 
a provision in the model runner for setting RNG seeds, but the downstream
scripts won't work with the resulting file names without some manual 
adjustment.

*****

## Overview

@@

Below are instructions for how to manually run the scripts in order to replicate the updated analysis. To do a clean replication, delete the `output/` folder; this is not required though.

@@

Anyways, the model runner script does include a provision for setting a RNG seed, in which case the key output files will be suffixed with the RNG seed value. Note that the results processing scripts are not setup to work this these output files. Instead of adjusting file names in the downstream scripts, the easiest way to get this working again is to copy the output + RNG seed files and rename them by dropping the RNG seed suffix.
